%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Staff Software Engineer} % Job title
    {Tableau Software} % Organization
    {Seattle, WA} % Location
    {Nov. 2012 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Unblocked a sales channel by delivering a solution for migrating customers between on-premise and SAAS products.}
        \item {Team member on a project which migrated Tableau Server from Ruby-on-Rails to a Java stack.}
        \item {Designed and delivered a lower latency search and browse experience for Tableau Server.}
        \item {Technical Lead and Architect for a team delivering a deployment and management framework for Tableau Server.}
        \item {Helped the sever team grow by 3x, through hiring, on-boarding and knowledge transfer to new developers.}
        \item {Technical leader for Tableau Server product. Collaborated with teams across the company for alignment of goals and architecture.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer II} % Job title
    {Amazon - Website Application Platform} % Organization
    {Seattle, WA} % Location
    {Nov. 2010 - Nov. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Technical leader on the Media Services platform team (Tier 1 Retail Service).}
        \item {Lead the migration and expansion of our video platform product.}
        \item {Re-architected the high scale index to be able to grow through Q4 2011 and 2012.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer/Test II} % Job title
    {Amazon - Retail Customer Experience} % Organization
    {Seattle, WA} % Location
    {Jun. 2009 - Nov. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a latency testing framework that could simulate various customer types (connection speeds and browsing environments).}
        \item {Built a latency rules system for automatically identifying common latency errors in multiple page types.}
        \item {Built a common test data repository that automatically categorized the most up to date data.}
        \item {Built a new sharing service for Selenium test servers. Allowed multiple teams to fairly share Selenium servers.}
        \item {Contributed to test automation for the Amazon Retail Detail Pages.}
        \item {Managed a Summer Intern.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer/Test II} % Job title
    {Microsoft - Windows Live} % Organization
    {Redmond, WA} % Location
    {Oct. 2005 - Jun. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed test strategies, and developed test automation, for shipping large features of the Windows Live Messenger Service.}
        \item {Gold Star (management award) for supporting external customers during an outage period while still delivering my assigned work.}
        \item {Member of the team who shipped the Messenger to Yahoo interop feature.}
        \item {Part of the team that built a service, which scaled to tens of millions of simultaneous online connections.}
        \item {Build a new high-scale client library for effective testing of the messenger service.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Programmer}
    {Vircom}
    {Perth, Western Australia}
    {Aug. 2004 - Aug 2005}
    {
      \begin{cvitems}
        \item {Worked on a team delivering monitoring and reporting tools for utility services.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Programmer}
    {CR2}
    {Perth, Western Australia}
    {May 2003 - Aug 2004}
    {
      \begin{cvitems}
        \item {Worked on a team delivering Channel Banking Sub-Host software, ATM software, and card network interfaces.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
